Predictive Modeling of Drinking Water Treatment Process Chemical Doses

### 2025-12-04 Paper Draft.Rmd
Added section on classification algorithms.

[Background on Drinking Water Treatment/Process Overview]

@@

@@

@@

>>>>

The drinking water treatment process takes water from a river, lake, reservoir, or other source, and purifies it to have it reach drinking water standards.

There are four primary steps of the water treatment process:  
1. Coagulation  
2. Flocculation  
3. Filtration  
4. Disinfection

@@

### Data Overview

@@

### Data Cleaning

@@

### Classification of Dose Change

We added two variables called `dose_change_FeCl` and `dose_change_Poly` that indicate
whether the chemical dose was increased, decreased, or stayed the same. Additionally, we
added variables indicating change in temperature, pH, turbidity, and conductivity from
the previous day.

This will allow classification methods to be applied. Additionally, if effective,
this could provide a more helpful tool for operators. Instead of attempting to 
predict a specific dose, it could give a general direction for an operator to 
attempt a dose change. This is how plants work in practice: an operator uses 
some tool (a water test, a reading from a device, etc.), and uses that to make 
a dose change. They then check important treatment metrics and make any needed
further adjustments.

```{r}

```
